---
output:
  pdf_document: default
  html_document: default
---
# Data transformation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
DT::renderDataTable({DT::datatable(data(), options=list(scrollX=TRUE))})
```

## Brief View of the Dataset
There is a brief view of the first 20 rows of the dataset.
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(readr)
library(DT)
vgsales = read_csv("vgsales-12-4-2019.csv")
datatable(head(vgsales,20))
```




## Extracting Specifc Variables for Each Question

We are extracting variables that help us to better understand and answer the three questions seperately. 

### Extraced Dataset for Question 1

In order to explore the impact of the platform to the video games and the trend over time, we are creating a dataframe that contains varibles "Platform"  "Global_Sales"   "NA_Sales"   "PAL_Sales"  "JP_Sales"   "Other_Sales" ,and "Year" .
```{r}
dataset1 = vgsales[,c("Platform","Global_Sales" , "NA_Sales"    , "PAL_Sales" , "JP_Sales" ,"Other_Sales","Year" )]
```


These are the platforms that release video games.
```{r}
levels(factor(dataset1$Platform))
```


### Extraced Dataset for Question 2


### Extraced Dataset for Question 3

We want to compare the top five popular video games and genres in North America and Japan. Then we need to include varibles "Name" "Genre" "Global_Sales","JP_Sales".
```{r}
dataset3 = vgsales[ ,c("Name", "Genre", "Global_Sales", "JP_Sales")]
```