---
output:
  pdf_document: default
  html_document: default
---
# Data transformation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## All the variables in the dataset
These are the avalible variables from the dataset.
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(readr)
vgsales = read_csv("vgsales-12-4-2019.csv")
colnames(vgsales)

#library(DT)
#datatable(vgsales)
```




## Extracting Specifc Variables for Each Question

We are extracting variables that help us to better understand and answer the three questions seperately. 

### Extraced Dataset for Question 1

In order to explore the impact of the platform to the video games and the trend over time, we are creating a dataframe that contains varibles "Platform"  "Global_Sales"   "NA_Sales"   "PAL_Sales"  "JP_Sales"   "Other_Sales" ,and "Year" .


These are the platforms that release video games.
```{r}
q1 = vgsales[,c("Platform","Global_Sales" , "NA_Sales"    , "PAL_Sales" , "JP_Sales" ,"Other_Sales","Year" )]
#View(q1)
levels(factor(q1$Platform))
```


### Extraced Dataset for Question 2


### Extraced Dataset for Question 3




